%%----------------------------------------------------------------------
%%----------------------------------------------------------------------
\missiontitle{The Cataclysm}

\begin{columns}
  
  All of the recon squads have crossed paths as they fight toward
  their final missions!

  The alliance with fewer total points earned in the Recon Squad
  matches is considered the {\bf Defender}, and the other alliance the
  {\bf Attacker}.

  \missionheading{Heroes}

  Before the game begins, the specialists in each player's recon squad
  are elevated to be independent characters.  Each leader additionally
  gains~1 Wound, is considered to be an HQ unit, and is their player's
  warlord.  The warlords receive a warlord trait as usual, and players
  may reroll randomly chosen traits.

  Before any deployment, each alliance declares one of their warlords
  to be their warmaster.

  \missionheading{The Battlefield}

  Deployment zones are the areas up to~12'' from the long table edges
  and along their length (Dawn of War).  The defender chooses a zone
  and the attacker takes the other, both taking the long edge of their
  zone as their player table edge.  The defender then places~3 primary
  objective markers in its deployment zone, after which the attacker
  places~3 in its zone.

  After all deployment (before any Scout redeployments), each player
  places a secondary objective marker, alternating sides beginning
  with the defender.

  The defender chooses to play first or second.

  \missionheading{Mission Rules}

  Night Fighting, Seize the Initiative, and Reserves all apply as in
  the standard Eternal War missions.  The Cataclysm ends after game
  turn~5.

  \missionheading{Scoring}

  Objective markers are scored after each game turn: Primaries award
  the current turn number in victory points, while secondaries award~1
  victory point.

  % \begin{itemize}
  % \item Primaries award the current turn number in victory points;
  % \item Secondaries award~1 victory point.
  % \end{itemize}

  Alliances gain~2 victory points if the opposing warmaster is removed
  as a casualty, and~1 victory point for each other opposing warlord
  eliminated.

  First Blood and Linebreaker both apply as in the standard Eternal
  War missions.

  % The first unit (including single models) to be removed in its
  % entirety for any reason yields~1 victory point to the opposing
  % alliance for first blood.  If an alliance has any scoring units in
  % its opponent's deployment zone at game end then it scores~1 victory
  % point for linebreaker.

  Whichever alliance scores the most victory points wins a tactical
  victory in the Cataclysm, while the alliance that has more players
  achieve their legacy objectives wins a strategic victory.

\end{columns}
