%%----------------------------------------------------------------------
%%----------------------------------------------------------------------
\clearpage
\pagetitle{Missions}

\begin{columns}
  
  Army rules, legacies, and missions for the campaign are in this
  section and should be read by all players.

\missionheading{Campaign}

The campaign consists of four rounds of Recon Squad skirmish matches,
followed by the Cataclysm, a climactic team battle.  Army construction
and gameplay rules for the Recon Squad rounds are here:

\smallskip
\centerline{\url{http://rocketshipgames.com/40k/recon-squad/}}

\smallskip%
The Cataclysm uses standard 40k gameplay rules except as described in
this packet.

At the start of the campaign, players join an alliance and choose a
legacy.  Legacies cannot be repeated within an alliance until all have
been chosen.  In each of the Recon Squad rounds, the alliances
alternate choosing missions from those in this section.

\missionheading{Army Construction}

Each player must prepare two lists:

\begin{itemize}\shortlist
  \item {\bf Recon Squad:} For the skirmish missions;
  \item {\bf Cataclysm:} For the climactic final team battle.
\end{itemize}

Recon Squad lists are selected to at most~200 points, following the
rules in that packet.  Cataclysm lists are selected to at most~500
points by these rules:

  \begin{itemize}\shortlist
  \item Each player's Recon Squad list must be included in their
    Cataclysm list in its entirety.

  \item Additional units and models (with wargear and upgrades) may be
    added to the Recon Squad Detachment.  However, the original models
    may not receive new wargear or upgrades.

  \item A single Cataclysm Reinforcements Detachment may be added to
    the army, with a force organization of~0--1 HQ,~1--3 Troop,~0--1
    Elite,~0--1 Fast Attack,~0--1 Heavy Support, and~0--1
    Fortification.  All its units must be chosen from a single
    faction, but that may be a different faction from the Recon Squad
    Detachment.

  \item No models with more than~3 wounds/hull points.

  \item No vehicles with total armor (front + side + rear) of more
    than~33.

  \item No models with both a~2+ Armor and~3+ Invulnerable save or
    better are permitted.

  \item No flyers, flying monstrous creatures, superheavy vehicles,
    gargantuan creatures, or mighty bulwarks are permitted.

  \item No psykers of mastery level~2 or greater.

  \item No unique independent characters or unique wargear is
    permitted.
  \end{itemize}

\missionheading{Recon Squad Mission Rules}
The Recon Squad missions use the following rules:

\begin{itemize}\shortlist
\item Matches are played on~4''x4'' tables.

\item The Variable Game Length rule applies.

\item If either player wishes the game to be a night fight, roll a~D6
  before any deployment begins. Night Fighting is in effect (all units
  have Stealth) for game turn~1 on a~4+; on a result of~1 Night
  Fighting takes effect for turn~5 and thereafter.

\item Unless specifically noted otherwise by the mission, deployment
  and turn order follows the standard rules: The winner of a D6 roll
  off decides to deploy first or second. After both players deploy,
  the player that deployed first chooses to play first or second. The
  player to go second may attempt to Seize the Initiative.

% Match results are worth the following campaign points. mostly relevant just to the larger narrative: A major victory outcome is worth 10 campaign points to the winner and 0 to the not-winner. Minor victory outcomes award 7 and 3 campaign points respectively. Draws award 5 campaign points to each player. Two additional bonus points are available in each mission, and if achieved are awarded regardless of victory or not. Better victories trump other results, e.g., meeting the conditions for a major victory renders the minor victory and draw conditions irrelevant.
\end{itemize}

\end{columns}

%%----------------------------------------------------------------------
%%----------------------------------------------------------------------

\vfill
\noindent
\begin{minipage}[t]{1.0\linewidth}\centering%
\rowcolors{2}{gray!12}{white}\setlength{\tabcolsep}{3pt}%
\resizebox{\linewidth}{!}{\begin{tabular}{|l|C{1in}|C{1in}|C{1in}|C{1in}|C{1in}|C{1in}|C{1in}|C{1in}|}
\hline
\rowcolor{gray!25} {\bf Mission}       
                    & {\bf Bodyguards}  & {\bf Excavators}& {\bf Headhunters}   & {\bf Killers}   & {\bf Penetrators}&{\bf Scouts}   & {\bf Sentinels} & {\bf Warriors}\\
\hline
\hline
{\bf Ambush}        & Defender          & Either         & Attacker             &                 &                 & Attacker       &                 &               \\
{\bf Assassination} & Defender          &                & Attacker             &                 & Attacker        &                &                 &               \\
{\bf Battlefield}   &                   &                &                      & Either          &                 &                &                 & Either        \\
{\bf Breakthrough}  & Attacker          &                &                      &                 & Attacker        &                & Defender        &               \\
{\bf Encirclement}  &                   &                &                      & Attacker        &                 &                & Defender        & Defender      \\
{\bf Excavation}    &                   & Either         & Either               &                 &                 & Either         &                 &               \\
{\bf Installation}  &                   & Either         &                      &                 & Attacker        &                & Defender        &               \\
{\bf Skirmish}      &                   &                &                      & Either          &                 & Either         &                 & Either        \\
\hline
\end{tabular}}

\small\it\smallskip
Recon Squad mission and role requirements for the legacies.
\end{minipage}
