%%----------------------------------------------------------------------
%%----------------------------------------------------------------------
\clearpage
\pagetitle{Organization}

\begin{columns}

This section describes how to conduct a \emph{Legacies} campaign, and
is mostly intended for the organizer.

\missionheading{Schedule}

Recon Squad games can be easily run in about~60 minutes in an event
setting with boards pre-arranged and armies unpacked before the clock
starts for each round.  Generally matches take at most~90 minutes even
at a very casual pace with no preparation beforehand.  The Cataclysm
game can be comfortably played in~3--4 hours.  It's therefore feasible
to run \emph{Legacies} over either several evenings, or a single full
day.  A sample schedule for a single-day is as follows.

\bigskip
\centerline{\begin{tabular}{cl}
11:00	 	& Doors open\\
11:50	 	& Registration Closes\\
12:00	 	& Campaign Briefing \& Alliance Pairings\\
12:15	 	& Round 1\\
1:25	 	& Alliance Pairings\\
1:35	 	& Round 2\\
2:40	 	& Alliance Pairings\\
2:50	 	& Round 3\\
3:50	 	& Alliance Pairings\\
4:00	 	& Round 4\\
5:00	 	& Dinner Break\\
5:30	 	& The Cataclysm\\
9:30	 	& Campaign Outcome \& Prizes\\
\end{tabular}}

\missionheading{Alliances \& Story}

At the start of the campaign, the players are organized into two
alliances with an equal number of players.  In some groups this might
be faction specific, e.g., Chaos Daemons versus Eldar.  Generally
though an alliance will be comprised of several factions and can be
given a less specific title such as the Forces of Order, Legions of
Discord, or the Spoiler Horde.  How players are assigned alliances is
up to the organizer.  In a large event with mostly strangers and
tournament leanings it might be simply random.  In more
narrative-oriented and casual settings though, some attempt should be
made to take into account thematic cohesiveness as well as balanced
skill levels.

The concept behind the campaign is that each recon squad is a team of
veterans or other distinguished warriors tasked with several special
operations as part of a larger battle or war.  In the course of those
missions their paths eventually all cross, resulting in the larger
final battle.  Any specific background story is up to the organizer
and players, enabling a range of narratives with more or less detail.

\missionheading{Setup}

In advance of the campaign, players should at a minimum read the Recon
Squad rules and select their army list.  They should also be pointed
to the \emph{Legacies} Mission Pack, or this whole packet, in case
they wish to tailor their squad toward a particular legacy.

Preparing for the campaign is very simple.  For each of the two
alliances, print and cut apart enough sets of the~8 legacy cards at
the end of the Mission Pack section to have at least one card per
player.  Also print and cut apart enough sets of the~8 mission sheets
to have one for each match.  For a campaign with up to~16 players this
means making two sets of legacy cards and one set of mission sheets.

\missionheading{Legacies}

After being assigned an alliance, each player chooses a legacy.  No
legacy may be selected twice within an alliance until all legacies
have been chosen at least once, and so on if there are even more
players.  Otherwise the alliance members may discuss among themselves
how to divy up the legacies.  If there is any contention, either ask
the players in random order to choose, or randomly assign legacies.

Each legacy lists three Recon Squad Missions and gives a Cataclysm
Objective and Legacy Bonus.  To achieve their legacy, players must
accomplish the Cataclysm Objective in the final team battle.  If they
win at least two of the three Recon Squad Missions in the given role
of attacker, defender, or either, then they receive their Legacy Bonus
in the Cataclysm.

Players' chosen legacies, match results, and whether or not they are
succeeding at their missions are all public information throughout the
campaign.

\missionheading{Round Pairings}

Match pairings are made strategically by the alliances to help their
players achieve their legacy missions and further their collective
strategic goals.  Before each round, the alliances alternate
nominating one of their remaining unpaired players along with a
mission and role (attacker or defender).  The opposing alliance then
responds with a player for the match, who takes the other mission role
and chooses an unclaimed game board to play on.  This player must be
in the same or best similar win/draw/loss bracket as the nominated
player, unless the number of players is not great enough to make this
restriction without repeating match pairings.  In that case the later
rounds might require specific pairings to not have repeats.

For the first round, the initial alliance to put a player forward is
determined either randomly or based on the background story or the
outcomes of connected preceding events.  In subsequent rounds the
alliances alternate making the initial nomination.

Players should use the checkboxes on their legacy cards to record
victories toward the Recon Squad Mission requirements, in addition to
the organizer keeping track.  It does not matter if the player was
nominated or the responding opponent, and they do not have to complete
the missions in any order.  In order to get their Legacy Bonus in the
Cataclysm they simply have to win each mission in the required role at
some point in the campaign.  Similarly, a player can attempt a mission
and role pair multiple times.  However, no advantage is gained by
winning the same mission and role pair multiple times.

\end{columns}

%%----------------------------------------------------------------------
%%----------------------------------------------------------------------
\vbox to 0pt{}
\vfill
\noindent
\begin{minipage}[t]{1.0\linewidth}\centering%
\rowcolors{2}{gray!12}{white}\setlength{\tabcolsep}{3pt}%
\resizebox{\linewidth}{!}{\begin{tabular}{|l|C{1in}|C{1in}|C{1in}|C{1in}|C{1in}|C{1in}|C{1in}|C{1in}|}
\hline
\rowcolor{gray!25} {\bf Mission}       
                    & {\bf Bodyguards}  & {\bf Excavators}& {\bf Headhunters}   & {\bf Killers}   & {\bf Penetrators}&{\bf Scouts}   & {\bf Sentinels} & {\bf Warriors}\\
\hline
\hline
{\bf Ambush}        & Defender          & Either         & Attacker             &                 &                 & Attacker       &                 &               \\
{\bf Assassination} & Defender          &                & Attacker             &                 & Attacker        &                &                 &               \\
{\bf Battlefield}   &                   &                &                      & Either          &                 &                &                 & Either        \\
{\bf Breakthrough}  & Attacker          &                &                      &                 & Attacker        &                & Defender        &               \\
{\bf Encirclement}  &                   &                &                      & Attacker        &                 &                & Defender        & Defender      \\
{\bf Excavation}    &                   & Either         & Either               &                 &                 & Either         &                 &               \\
{\bf Installation}  &                   & Either         &                      &                 & Attacker        &                & Defender        &               \\
{\bf Skirmish}      &                   &                &                      & Either          &                 & Either         &                 & Either        \\
\hline
\end{tabular}}

\small\it\smallskip
Recon Squad mission and role requirements for the legacies.
\end{minipage}
\vfill


%%----------------------------------------------------------------------
%%----------------------------------------------------------------------
\clearpage

\begin{columns}


\end{columns}


%%----------------------------------------------------------------------
%%----------------------------------------------------------------------
\clearpage
\pagetitle{The Twilight: Mission Pack}


All of the missions are played on a~4'x4' table.

The variable game length rule is used in all missions unless noted otherwise.

  Roll a~D6 before any
deployment.  Night Fighting is in effect for Turn~1 on a~4+; on a~1
or~2 it takes effect on Turn~5 and thereafter.

The winner of a~D6 roll off decides to deploy first or second.  After
both players deploy, the player that deployed first chooses to play
first or second.  The player to go second may attempt to Seize the
Initiative.


A major victory is worth 10 points to the winner and 0 to the loser.
Victory is 7 and 3
Draw is 5 and 5

Plus the two bonus points.

Better victories trump others, e.g., meeting the conditions for a
major victory trumps the conditions for a minor victory.

Missions to be specified in more detail...

\missionheading{Ambush}

The Defender is given an AV10/10/10 HP2 truck with 5 embarked NPCs
with sub-Guardsman stats.  The truck takes dangerous terrain tests on
a 2+ and always takes a dangerous terrain test if it moves flat out.
The truck starts at one end of the board and it or the NPCs must make
it to the far edge.  The Attacker Outflanks.


\missionheading{Assassination}

An NPC with Guardsman-ish stats is placed in control of the Defender,
who loses if it dies.


\missionheading{Battlefield}

Kill points with Dawn of War setup.


\missionheading{Breakthrough}

Attacker has to break into the defender's deployment zone.


\missionheading{Encirclement}

Kill points with the defender starting at the center of the table and
the attacker all around.


\missionheading{Excavation}

Similar to the scouring, several objectives of randomized value are
randomly placed inside a square at table center.  The defender starts
deployed in that square, the attacker is around the edges.


\missionheading{Installation}

A single objective is put forward slightly from the defenders leading
edge, inside an AV11 HP3 Small building.  The defender wins if they
hold that objective.  Otherwise the attacker wins.


\missionheading{Skirmish}

The basic mission from the Recon Squad packet: Vanguard and three objectives.
