\clearpage
\thispagestyle{empty}
\squelchbackground

\noindent%
\legacycard{BODYGUARDS}%
{Our lives for you, my liege.\\~}%
{Ambush}%
{Defender}%
{Assassination}%
{Defender}%
{Breakthrough}%
{Attacker}%
{After all deployment, publicly pledge to defend one of your alliance's
  warlords other than your own.  You succeed if that warlord is on the battlefield at game end (i.e., survived and not embarked).}%
{Whenever your pledged warlord
loses a wound, on a~D6 of ~2+ the loss may be cancelled by one of your non-Vehicle
models within~3'' taking a mortal wound instead.}
%%
\hfill
%%
\legacycard{EXCAVATORS}%
{Get it into the crates,\\quickly, this is ours!}%
{Ambush}%
{Either}%
{Excavation}%
{Either}%
{Installation}%
{Either}%
{After all deployment ends, secretly select an objective marker wholly
  outside your deployment zone.  You succeed if you control that objective marker at game
  end.}%
{Any single non-Vehicle model of yours that starts the movement
  phase in contact with \emph{any} marker may move it up to~6'' with
  the model's movement.  The marker cannot leave the table, including to embark a Transport.}


\noindent%
\legacycard{HEADHUNTERS}%
{Death comes for us all.\\We come for you.}%
{Ambush}%
{Attacker}%
{Assassination}%
{Attacker}%
{Excavation}%
{Either}%
{After all deployment, secretly select one of the opposing warlords.
  You succeed if that warlord is not in play at game end.}%
{Your non-Vehicle models may shoot at that warlord regardless of
it being the closest enemy or not.}
%%
\hfill
%%
\legacycard{KILLERS}%
{Kill.  Maim.  Burn.\\~}%
{Battlefield}%
{Either}%
{Encirclement}%
{Attacker}%
{Skirmish}%
{Either}%
{After all deployment, publicly declare a crusade against an opposing
  player.  You succeed at game end if at most 25\% of that player's
  starting army points remain in play (i.e., they have at most 125pts).}%
{In the fight phase your non-Vehicle models receive a~+1 to hit against that opponent's units.}

\pagebreak
\thispagestyle{empty}

\noindent%
\legacycard{PENETRATORS}%
{Everything has a weak spot.\\~}%
{Assassination}%
{Attacker}%
{Breakthrough}%
{Attacker}%
{Installation}%
{Attacker}%
{At game end your units control at least one primary objective marker
  in the opposing deployment zone.}%
{After all deployment ends you may ruin a piece of terrain or opposing fortification,
reducing any associated cover by~1 (to~+0 at worst).}
%%
\hfill
%%
\legacycard{SCOUTS}%
{Let's go, on the move!\\~}%
{Ambush}%
{Attacker}%
{Excavation}%
{Either}%
{Skirmish}%
{Either}%
{Control at least three different objective
  markers outside your deployment zone at the end of any of your turns over the course of the game (not necessarily
  simultaneously).}%
% {At the end of each of your turns except the first, make a note for
%   each primary objective marker you control outside your deployment
%   zone which you have not previously controlled.  You succeed if you
%   note at least three.}%
%
{Your non-Vehicle units may deploy on maneuver
instead of on the battlefield.  At the end of any of your Movement phases they may be set up anywhere on the battlefield wholly within~6'' of a battlefield edge and more than~9'' from all enemy models.}

\vfill


\noindent%
\legacycard{SENTINELS}%
{None shall pass.\\~}%
{Breakthrough}%
{Defender}%
{Encirclement}%
{Defender}%
{Installation}%
{Defender}%
{At game end your units control all the primary objective markers that
  began in your deployment zone.}%
{After all deployment ends you may bolster a piece of terrain or a
  fortification in your deployment zone, improving any associated
  cover bonus by~1, to~+2 at best.}
%%
\hfill
%%
\legacycard{WARRIORS}%
{This isn't over.\\This will never be over.}%
{Battlefield}%
{Either}%
{Encirclement}%
{Defender}%
{Skirmish}%
{Either}%
{There are no enemy models in your deployment zone at
  game end.}%
{Whenever one of your non-Vehicle models loses a wound, the loss is cancelled
on a~D6 of~6+. If the model already had such a rule then the loss is cancelled on a~5+.}


\clearpage
\restorebackground
