%%----------------------------------------------------------------------
%%----------------------------------------------------------------------
\missiontitle{Mission: Ambush}

\begin{columns}

A supply convoy is moving through the area.

  {\bf Attacker:} You \emph{need} those supplies.

  {\bf Defender:} The supplies must get through.

\missionheading{The Battlefield}%

The winner of a~D6 roll off chooses a table edge and the other player
takes the opposite.  The defender's deployment zone is the~12'' strip
along their table edge.  All of the attacker's units gain Outflank and
must be placed in reserve, except Infiltrators which may deploy as
usual.  At the start of their deployment, the defender gains a convoy
vehicle for their army.

%Place a small vehicle with its forward edge~6'' from the
%defender's edge and center 24'' from the sides.

\missionheading{Mission Rules}%

%The attacker plays first.  The defender may not Seize the Initiative.

Half of the attacker's army by the number of models, rounding up,
arrives from reserve on Turn~1.  The remainder arrive from reserve as
usual.

The convoy vehicle has armor~11/11/10,~3 hull points, and may not move
Flat Out.  It ignores all results on the Vehicle Damage table, only
losing the hull point when damage is incurred.  On a failed dangerous
terrain test it loses a hull point and cannot move further that phase
but is not immobilized.  The vehicle, or its wreck, also acts as an
objective marker.  While the vehicle is not destroyed, the defender
controls it by default if there are no attacker models within 3''.

% At game start it is controlled by the
% defender.  Either player may take control of the vehicle by ending
% their turn with they alone having an unengaged model in base contact.
% Models do not need to remain in contact to keep control.

%If
%immobilized, the vehicle self-repairs and removes that damage result
%on a~D6 of~4+ at the start of the defender's movement phase.

%At game end, victory points are earned as follows:
%
%\begin{squishitemize}
%\item Each player gets~2 victory points for each~12'' the vehicle is
%  from their edge, rounding down.
%
%\item At least 50\% of the opponent's army by points value or number
%  of models are casualties: +2
%
%\item All of the opponent's models have been removed as casualties: +1
%\end{squishitemize}

%\vspace*{-17pt}

\scoringbox%
{Attacker if the vehicle is destroyed and they control its wreck.
  Defender if the vehicle or its wreck is within 12'' of the attacker
  table edge and they control it.}%
{Attacker if the vehicle is not destroyed but they control it.
  Defender if they control the vehicle or its wreck, but it is not
  within 12'' of the attacker table edge.}%
{The vehicle or its wreck is contested.}%
{Opponent's leader is a casualty.}%
{Player's leader survives.}

\end{columns}
