%%----------------------------------------------------------------------
%%----------------------------------------------------------------------
\clearpage
\section{Mission: Assassination}

  A VIP is touring the frontlines, their mission unknown.
  \begin{squishitemize}
  \item {\bf Attacker:} The VIP must be slain.
  \item {\bf Defender:} The VIP must be defended at all cost.
  \end{squishitemize}

\subsection{\bf The Battlefield}%

Deployment zones are 12'' from opposing table edges.  Place~3
objective markers at~12'' intervals along the centerline 24'' from
both player table edges.

\subsection{\bf Mission Rules}%

At the start of their deployment, the defender gains a VIP for their army:

\vspace*{-9pt}
\begin{center}    
  \begin{tabular}[t]{O{1.5in}cccccccccE{2.5in}}
    & {\bf M} & {\bf WS} & {\bf BS} & {\bf S} & {\bf T} & {\bf W} & {\bf A} & {\bf Ld} & {\bf Sv} & {\bf Keywords}\\
\hline
    {\bf VIP} & 6 & 4+ & 4+ & 3 & 3 & 6 & 2 & 10 & 4+ & Character, Infantry\\
  \end{tabular}
  \end{center}

  \vspace*{-9pt}
  \hfill
  \begin{minipage}{6in}
    \noindent\textbf{Refractor Field.} This model has a~5+ invulnerable
    save.

    \noindent\textbf{On Assignment.}  This unit is taken to have whatever
    faction keywords are shared by all of the units in your army list
    (all of the partners' lists in team games).
  \end{minipage}
  \hfill\hbox to 0pt{}

  At game end, each objective marker is worth~1 victory point.  The
  defender gets~2 victory points for each wound remaining on the VIP.
  The attacker gets~2 victory points for each wound lost by the VIP.

\vfill  
\scoringbox%
{Player has at least twice as many victory points as their opponent.}%
{Player has more victory points.}%
{Players have equial victory points.}%
{Opponent's leader is a casualty.}%
{Player has a model in opponent's deployment zone.}


