%%----------------------------------------------------------------------
%%----------------------------------------------------------------------
\missiontitle{Mission: Battlefield}

\begin{columns}

  The war grinds on interminably, all notion of battle lines lost in
  the confusion and exhaustion.

  \textbf{Attacker} and \textbf{Defender} roles are identical in this
  mission and have no effect in-game.

\missionheading{The Battlefield}%

The winner of a~D6 roll off chooses a table corner.  Their deployment
zone is the quarter circles of all points within~12'' of that corner
as well as the \emph{diagonally} opposite corner.  The other player's
deployment zone is the~12'' quarter circles from the other corners.

Place a single objective marker at table center.

% \vfill
% \vbox to 0pt{}
% \columnbreak

\missionheading{Mission Rules}%

At game end, victory points are earned as follows:

\begin{squishitemize}
\item At least~3 of your opponent's models have been removed as
  casualties: +2

\item At least 50\% of your opponent's army by points value or number
  of models are casualties: +3

\item The total number of wounds lost as a casualty by your opponent
  is more than you: +1

\item All of your opponent's models have been removed as casualties:
  +1
\end{squishitemize}

\vspace*{-2pt}

\scoringbox%
{Player has at least twice as many victory points as their opponent.}%
{Player has more victory points.}%
{Players have equial victory points.}%
{Opponent's leader is a casualty.}%
{Controls the objective marker.}

\end{columns}
