%%----------------------------------------------------------------------
%%----------------------------------------------------------------------
\missiontitle{Mission: Breakthrough}

\begin{columns}

  Opposing forces thrust and counter-thrust to break up or hold
  battlefield positions.

{\bf Attacker:} You must pierce the enemy's lines.

{\bf Defender:} Hold your ground.

\missionheading{The Battlefield}%

The winner of a~D6 roll off chooses a table edge and the other player
takes the opposite.  Deployment zones are~12'' from the players'
respective edges.

% , but the defender's models must all be placed at
% least~6'' from their player table edge.

% Place~4 objective markers,~6'' and~18'' from the two side edges and
% all 3'' from the defender table edge.

\missionheading{Mission Rules}%

At game end, victory points are earned as follows:

\begin{squishitemize}
\item The defender earns~2 victory points for each quarter of their
  army by number of models that has not been removed as a casualty,
  rounding down (i.e., less than~25\% is worth no points).

\item The defender earns~1 victory point if no attacker models are in
  the defender's table half.

\item The attacker earns~1 victory point for each quarter of their
  army by models that has not been removed as a casualty, rounding
  down.

\item The attacker earns~1 victory point for each quarter of their
  starting army by models that is at least partially within 6'' of the
  defender table edge, rounding up (i.e., having at least~1 model
  within 6'' of the defender edge is worth a point).

\end{squishitemize}

% \vfill
% \vbox to 0pt{}
% \columnbreak

\scoringbox%
{Player has at least twice as many victory points as their opponent.}%
{Player has more victory points.}%
{Players have equial victory points.}%
{Opponent's leader is a casualty.}%
{Leader is within 12'' of opponent's player table edge.}

% \scoringbox%
% {Attacker if they control at least~3 objective markers.  Defender if
% the attacker controls no objective markers.}%
% {Attacker if they control at least~1 objective marker.}%
% {Otherwise.}%
% {Opponent's leader is a casualty.}%
% {Player's leader is the closest model to the defender's table edge.}

% \scoringbox%
% {Attacker if at least~50\% of their starting army by number of models
%   is at least partially within~6'' of the defender's table edge.
%   Defender if attacker has no models within~6'' of the defender's
%   table edge.}%
% {Attacker if more than~25\% of their starting army by number of models
%   is at least partially within~6'' of the defender's table edge.
%   Defender if attacker has at most 25\% of their starting army by
%   points value or number of models within~6'' of the defender's table
%   edge.}%
% {Otherwise.}%
% {Opponent's leader is a casualty.}%
% {Player's leader is the closest model to the defender's table edge.}

\end{columns}
