%%----------------------------------------------------------------------
%%----------------------------------------------------------------------
\missiontitle{Mission: Excavation}

\begin{columns}

  An important relic was uncovered by an excavation team just before
  they were forced to abandon the site by the encroaching battle.  It
  must be retrieved!

  \textbf{Attacker} and \textbf{Defender} roles are identical in this
  mission and have no effect in-game.

\missionheading{The Battlefield}%

Deployment zones are 12'' from opposing table edges.  The winner of
a~D6 roll off chooses a side and the other player takes the opposite.

Place a primary objective marker at the center of the table and
secondary objective markers at the center of each table quadrant.


\missionheading{Mission Rules}%

Any model that starts the movement phase in base to base contact with
the \emph{primary} objective marker while no enemy models are in base
to base contact with it may move the marker with itself up to a total
of 6'' in the movement phase, ending in contact with the model.  The
marker cannot leave the table or embark.

%\columnbreak

At game end, control of the primary objective is worth~3 victory
points while each secondary objective is worth~1 victory point.

\scoringbox%
{Player controls the primary objective and has more victory points.}%
{Player has more victory points.}%
{Players have equal victory points.}%
{Opponent's leader is a casualty.}%
{The primary objective marker is fully within your deployment zone.}

\end{columns}
