%%----------------------------------------------------------------------
%%----------------------------------------------------------------------
\clearpage
\section{Mission: Installation}

  A critical outpost, command center, supply warehouse, or temple has
  come under siege!
  \begin{squishitemize}    
\item {\bf Attacker:} You must destroy it and control the site.

\item {\bf Defender:} You must protect the installation.
  \end{squishitemize}

\subsection{\bf The Battlefield}%

Deployment zones are 12'' from opposing table edges.

\subsection{\bf Mission Rules}%

At the start of their deployment, the defender gains a Comms Facility
for their army:

\vspace*{-9pt}
\begin{center}
  \begin{tabular}[t]{O{1.5in}cccccccccE{2.5in}}
    & {\bf M} & {\bf WS} &  {\bf BS} & {\bf S} & {\bf T} & {\bf W} & {\bf A} & {\bf Ld} & {\bf Sv} & {\bf Keywords}\\
\hline
    {\bf Comms Facility} & - & - & - & - & 8 & 12 & - & - & 4+ & Explodes\\
  \end{tabular}
  \end{center}

  The defender deploys first but the attacker plays first.  Seize the
  Initiative applies.  The Comms Facility cannot be placed within~6''
  of any table edge.  If the Comms Facility is destroyed, leave its
  model in place and treat it as an objective marker.

% Control of the building or its ruins is determined as an objective
% marker, including embarked models.


\vfill
\scoringbox%
{Attacker if the Comms Facility is destroyed and they control the wreckage.
  Defender if the Comms Facility is not destroyed and they control it.}%
{Attacker if the Comms Facility is destroyed but contested, or intact but
  they control it.  Defender if the Comms Facility is destroyed but they
  control the wreckage.}%
{Not applicable.  \emph{There is no middle ground in this mission.}}%
{Opponent's leader is a casualty.}%
{Less than 25\% of opponent's starting army remains, by
  number of models.}
